Sr: Processing Data Streams By Doing Less Work

### 2012-05-04 paper/paper.tex
Tilde thing for refs

The remainder of this paper is organized as follows. Section ~\ref{sec:relwork} provides an overview of related work on distributed stream processing as well as dynamic and approximate computations. Section ~\ref{sec:design} details how I designed Sr. Section ~\ref{sec:methodology} explains the methodology used to perform a cvase study using Sr. Section ~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.

@@

The master is the only well-known node in the cluster. Other nodes in the network exclusively communicate with the master. The master and other nodes communicate with each other by issuing HTTP requests to a simple server on each node. I decided to make use of a library [Sinatra.rb] providing the server functionality because there was a low barrier to getting inter-node communication functioning. This design choice presents some problems and will be discussed further in Section ~\ref{sec:discussion}.

@@

\section{Methodology}
\label{sec:methodology}
The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master. Roles are partitioned among nodes as shown in Figure ~\ref{fig:clusterDiagram}. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each. The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.

@@

Workers are initialized with the 3 computation routines shown in Table ~\ref{table:workerTasks}.

@@

The distribution shown in Figure ~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.

\subsubsection{Precision}
Task killing should least impact the head of the word distribution. Figure ~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate. Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.

@@

\subsubsection{Word Count Job Accuracy}
Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail. Figure ~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level). Setting the work level to 0.4 nets a greater increase in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times more than the fraction of words examined.

@@

Table ~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row with kill rate = 0.0 and work level = 1.0 represents the perfect, MapReduce-style, execution of the word count job. The only consistent reduction in execution time is a result of increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.

>>>>

The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides an overview of related work on distributed stream processing as well as dynamic and approximate computations. Section~\ref{sec:design} details how I designed Sr. Section~\ref{sec:methodology} explains the methodology used to perform a cvase study using Sr. Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.

@@

The master is the only well-known node in the cluster. Other nodes in the network exclusively communicate with the master. The master and other nodes communicate with each other by issuing HTTP requests to a simple server on each node. I decided to make use of a library [Sinatra.rb] providing the server functionality because there was a low barrier to getting inter-node communication functioning. This design choice presents some problems and will be discussed further in Section~\ref{sec:discussion}.

@@

\section{Methodology}
\label{sec:methodology}
The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master. Roles are partitioned among nodes as shown in Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each. The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.

@@

Workers are initialized with the 3 computation routines shown in Table~\ref{table:workerTasks}.

@@

The distribution shown in Figure~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.

\subsubsection{Precision}
Task killing should least impact the head of the word distribution. Figure~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate. Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.

@@

\subsubsection{Word Count Job Accuracy}
Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail. Figure~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level). Setting the work level to 0.4 nets a greater increase in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times more than the fraction of words examined.

@@

Table~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row with kill rate = 0.0 and work level = 1.0 represents the perfect, MapReduce-style, execution of the word count job. The only consistent reduction in execution time is a result of increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.
